Thermodynamic response functions in a cell fluid model

### 2024-09-12 paper_text.tex
add derivation of kappa_T in Appendix, mentioned it in text

Let us introduce the reduced isothermal compressibility
\begin{equation}
	\kappa^*_T \equiv \frac{\varepsilon K_T}{v}.
\end{equation}
The quantity $\kappa^*_T$ is dimensionless and is of order unity, except at the critical point itself, where it is divergent. It is expressed in terms of the reduced quantities $P^*$ and $\rho^*$ as follows
\begin{eqnarray}
	\kappa^*_T & = & \frac{\varepsilon}{{\rho^*}^2} \left(\frac{\partial \rho^*}{\partial \mu}\right)_T
	\nonumber\\
	& = & \frac{\varepsilon^2}{{\rho^*}^2} \left(\frac{\partial^2 P^*}{\partial \mu^2}\right)_T.
\end{eqnarray}
Now, either Eq.~\eqref{eq:eosPTM_reduced} or Eq.~\eqref{eq:density} can be used to explicitly calculate $\kappa^*_T$, with the result expressed as a function of temperature and chemical potential.

@@

>>>>

Let us introduce the reduced isothermal compressibility
\begin{equation}
	\kappa^*_T \equiv \frac{\varepsilon K_T}{v}.
\end{equation}
The quantity $\kappa^*_T$ is dimensionless and is of order unity, except at the critical point itself, where it is divergent. It is expressed in terms of the reduced quantities $P^*$ and $\rho^*$ as follows
\begin{eqnarray}\label{eq:kappa_star_m}
	\kappa^*_T & = & \frac{\varepsilon}{{\rho^*}^2} \left(\frac{\partial \rho^*}{\partial \mu}\right)_T
	\nonumber\\
	& = & \frac{\varepsilon^2}{{\rho^*}^2} \left(\frac{\partial^2 P^*}{\partial \mu^2}\right)_T.
\end{eqnarray}
Now, either Eq.~\eqref{eq:eosPTM_reduced} or Eq.~\eqref{eq:density} can be used to explicitly calculate $\kappa^*_T$, with the result expressed as a function of temperature and chemical potential. As an example, in Appendix~\ref{sec:app-a} we provide the derivation of the relation for the isothermal compressibility from the upper line of \eqref{eq:kappa_star_m}.

@@

As an example, we also give the derivation of the relation for the isothermal compressibility $\kappa^*_T$ from the upper line of \eqref{eq:kappa_star_m} recalling the density $\rho^*$ defined in \eqref{eq:density}.

For the effective chemical potential $M$ from \eqref{chem_pot} one has
\begin{equation}
\left(\frac{\partial M}{\partial \mu} \right)_T = \frac{1}{W(0)}.
\end{equation}
For the quantity $\bar \rho_0$ from \eqref{eq:ro_MT} one has
\begin{equation}
\left(\frac{\partial \bar \rho_0}{\partial \mu} \right)_T = \frac{1}{ g_4 W(0) \sqrt{Q_t}} \left( \bar \rho_0 - 2 \left[ - \frac{3M}{g_4} + \sqrt{Q_t} \right]^{\frac{1}{3}} \right).
\end{equation}
Using these two formulas we obtain the isothermal compressibility in explicit form  
\begin{eqnarray}
&&	\kappa_T^* = \frac{\epsilon}{\rho^{*2} W(0)} \nonumber \\
&& \times \left\{  \frac{1}{\beta W(0) g_4 \sqrt{Q_t}} \left( \bar \rho_0 - 2 \left[ - \frac{3M}{g_4} + \sqrt{Q_t} \right]^{\frac{1}{3}} \right) - 1 \right\}.
\end{eqnarray}
